% Ava Scherocman's Resume
% LaTeX template and class from rpi.edu

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Ava Scherocman}
 \moveleft.5\hoffset\centerline{ Computer Science Student at The Ohio State University}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{(513)-609-8320}
 \moveleft.5\hoffset\centerline{ava@scherocman.com}
 \moveleft.5\hoffset\centerline{she/her/hers}


\begin{resume}

\section{EXPERIENCE} 
 
                 {\bf Collaboration and Power Platform Intern} \hfill        Summer 2022 \\
                Interlink Cloud Advisors, Mason, OH
                  \begin{itemize}
                   \item Optimized existing internal company processes and built tools for customers using Microsoft Power Platform software.
                   \item Built Human Resources division of company intranet using Microsoft Modern SharePoint and Power Platform software.
                   \end{itemize} 
                {\bf Mobile Software Development Intern} \hfill        Summer 2021 \\
                Kroger Technology, Remote/Cincinnati, OH
                  \begin{itemize}
                    \item Worked in Swift and SwiftUI fixing design and logical  issues in the iOS version of the Kroger app. 
                    \item Added maps and real-time location tracking to five hundred Kroger brand family stores across the United States.
                    \item Provided a convenient shopping experience to customers through the Kroger app's ‘Store Mode’.
                   \end{itemize} 
                {\bf Information Systems Intern} \hfill Summer 2020\\
                GMi Companies, Lebanon, OH
                \begin {itemize}
                    \item  Wrote code in C/AL using Dynamics NAV to add new features to manufacturing production systems.
                    \item  Improved program code resulting in a 6x increase in inventory system productivity.
                \end{itemize}
                 {\bf Marketing Intern  } \hfill Summer 2019\\
               Hack Club, Remote/San Francisco, CA
                \begin {itemize}
                    \item  Recruited high school students and teachers over email and phone to found over fifty local student-led computing clubs.
                    \item Helped active club leaders take advantage of the benefits of a company partnership with GitHub.
                \end{itemize}
 

\section{EDUCATION} Bachelor of Science in Computer Science and Engineering\\
                Ohio State University, expected May 2025 \\
                Minor in Statistics
                
 
 
\section{COMPUTER \\ SKILLS} Java, C++, HTML/CSS, C/AL, Microsoft Power Automate, Microsoft Power Apps, Dynamics NAV, Visual Basic.NET, Visual Basic 6, GeoJSON, Jira, Swift, ConnectWise Manage, \LaTeX


\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            \textit {Community Outreach Coordinator}, ACM-W at OSU\\
            \textit {Treasurer}, Dance Coalition at OSU\\
            \textit {Executive Director}, Mason Hack Club\\
            \textit {President}, Mason High School ACM\\
            \textit {Volunteer}, Girl Scouts of Western Ohio
 

\end{resume}
\end{document}




